Click chemistry reveals an alternate mechanism for HPII catalase

### 2018-02-18 bb494/manuscript.tex
commit

\section{Results}
DH10B cell lines with appropriate plasmids were grown for 48h and pelletized. Wildtype HPII-containing cells were purified using TALON resin. Purified wildtype protein and ncAA cell lysates are shown in Figure \ref{fig:crude-wt-gel}. The expected band corresponding to an 84-kD protein is seen across all lanes, verifying the presence of HPII wildtype in all cultures. Contaminant bands in the gel are very faint, indicating pure protein.\\

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/crude-wt-gel}
\caption{Electrophoresis gel of wildtype expression. Serial dillution of WT protein purification shown in lanes three and four. Major band in purification lanes correspond to protein of approximately 80kD, as expected for a catalase single subunit. }
\label{fig:crude-wt-gel}
\end{figure}

>>>>

\section{Results}
DH10B cell lines with appropriate plasmids were grown for 48h and pelletized. Wildtype HPII-containing cells were purified using TALON resin. Purified wildtype protein and ncAA cell lysates are shown in Figure \ref{fig:pure-gel}. The expected band corresponding to an 84-kD protein is seen across all lanes, indicating the presence of a catalase single subunit in each cell line. Contaminant bands in the gel are very faint, indicating pure protein.\\

@@

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{figures/pure-gel}
\caption{Electrophoresis gel of crude lysate and purified protein expression. Major band in purification lanes correspond to protein of approximately 80kD, as expected for a catalase single subunit. Crude negative control lanes lack 80kD band, consistent with noncanonical amino acid being necessary for noncanonical protein expression.}
\label{fig:pure-gel}
\end{figure}
